The Effect of Authoritarian Legislature on Regime-Opposition Interaction

### 2014-12-03 writeups/prelim_presentation.tex
more tweaks

\title[Effect of Authoritarian Legislature]{The Effect of Authoritarian Legislature on Regime-Opposition interaction} % The short title appears at the bottom of every slide, the full title is only on the title page

@@

\section{Theory}
\begin{frame}
\frametitle{Regime-Opposition Bargaining Game}
\begin{itemize}
\item Violence is the final arbiter in authoritarian politics
\item Regime-opposition interaction is best modeled as a bargaining game, similar to the bargain between two sovereign states with the option of going to war
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{The Model}
\centering
\begin{itemize}
\item Negotiation about the share $x$ ($0 < x < 1$) of a good given to the opposition
\item Violence costs the autocrat $c_A$ and the opposition $c_O$
\item Expected utility depends on the probability of the opposition winning, $p$
\item<2-> Violence should never happen since $x$ that falls within the bargaining range $(p - c_O, p + c_A)$ is preferable to both sides
\end{itemize}
\includegraphics[width=0.7\textwidth]{general_model}
\end{frame}

@@

\begin{frame}
\frametitle{The Model}
However, authoritarian legislature solves all of these issues
\begin{itemize}
\item Elections and legislative session provide information about both sides' capacity
\item Cost of violent uprising and repression is increased relative to negotiation
\item Negotiations over multiple issues in the legislature enable side payments
\end{itemize}
\end{frame}
\section{Experimental Design}
%------------------------------------------------
\begin{frame}
\frametitle{Experimental Design}

@@

\frametitle{Co-variate Balance}

@@

\adjustbox{max height=\textheight,

@@

}

@@

\onslide<2->
\adjustbox{max height=\textheight,

@@

\begin{frame}
\frametitle{Empirical strategy}
\begin{itemize}
\item Create short panels of four country years
\item Treatment panel: no legislature in the first year, legislature in the next three years
\item Control panel: no legislature throughout the panel
\item Match panels based on the co-variates of the first years
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Matching result}
\centering
\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
           max width=\textwidth}{
\begin{tabular}{lrrlrrrl}
  \hline
 & \multicolumn{3}{c}{Pre-Match} &   \multicolumn{3\textbf{}}{c}{Post-Match} \\
Covariate & Treated & Control & p-value & Treated & Control & p-value &  \\ 
  \hline
Ethnic Fractionalization & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
$\text{Violence}^2$ & 29.84 & 23.22 & 0.34 & 29.84 & 29.03 & 0.65 &  \\ 
Regime duration (years) & 12.08 & 34.30 & 0.00*** & 12.08 & 12.71 & 0.71 &  \\ 
$\text{Regime duration}^2$ & 278.00 & 2783.57 & 0.00** & 278.00 & 287.38 & 0.89 &  \\ 
Military & 0.08 & 0.06 & 0.67 & 0.08 & 0.12 & 0.57 &  \\ 
Monarchy & 0.04 & 0.25 & 0.00*** & 0.04 & 0.04 & 1.00 &  \\ 
Party & 0.29 & 0.48 & 0.07* & 0.29 & 0.29 & 1.00 &  \\ 
log(gdp) & 22.65 & 23.95 & 0.00*** & 22.65 & 22.78 & 0.67 &  \\ 
log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
Military expenditure (\%GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
Resource Export (\%GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 & \\
  \hline
\end{tabular}
}
\end{frame}

\begin{frame}
\frametitle{Matching result}
\centering
\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
           max width=\textwidth}{
\begin{tabular}{lrlr}
  \hline
 \multicolumn{2}{c}{Treatment} &   \multicolumn{2}{c}{Control} \\
Country & Year & Country & Year \\ 
  \hline
Algeria & 1996 & Sudan & 1992 \\ 
  Angola & 1992 & Angola & 2000 \\ 
  Azerbaijan & 1992 & Uganda & 1991 \\ 
  Belarus & 2004 & Belarus & 2000 \\ 
  Cambodia & 1993 & Laos & 1999 \\ 
  Central African Republic & 2005 & Uganda & 2001 \\ 
  Chad & 1997 & Central African Republic & 1992 \\ 
  Congo, Republic & 2002 & Nigeria & 1994 \\ 
  Congo, Dem Rep & 2006 & Congo, Dem Rep & 1996 \\ 
  Ethiopia & 1995 & Ethiopia & 1993 \\ 
  Gambia & 1996 & Belarus & 2001 \\ 
  Ghana & 1995 & Belarus & 2000 \\ 
  Jordan & 1993 & Swaziland & 2007 \\ 
  Kazakhstan & 1995 & Sudan & 1994 \\ 
  Kenya & 1992 & Laos & 1997 \\ 
  Kyrgyzstan & 1995 & Belarus & 1998 \\ 
  Pakistan & 2002 & Algeria & 1993 \\ 
  Rwanda & 2003 & Rwanda & 1999 \\ 
  Sudan & 2000 & Sudan & 2006 \\ 
  Tajikistan & 1995 & Belarus & 1999 \\ 
  Tanzania & 1995 & Sierra Leone & 1992 \\ 
  Togo & 1994 & Togo & 1991 \\ 
  Uganda & 2006 & Uganda & 1998 \\ 
  Uzbekistan & 1999 & Ethiopia & 1993 \\ 
   \hline
\end{tabular}
}
\end{frame}

\begin{frame}
\frametitle{Multilevel model}
\begin{alignat*}{2}
&{event}_i &&\sim N(\alpha^{countryyear}_{j[i]} + A \cdot \text{sector}_i, \sigma^2_{event}) \\
&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{legis}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
&\beta_k^{country} &&\sim N(\delta_0 + \delta_{ethnic} \cdot \text{ethnic}_k + D \cdot \text{region}, \sigma_\beta^2) 
\end{alignat*}
\end{frame}

>>>>

\title[Effect of Authoritarian Legislature]{The Effect of Authoritarian Legislature on Regime-Opposition Interaction} % The short title appears at the bottom of every slide, the full title is only on the title page

@@

\section{Theory}
\begin{frame}
\frametitle{Regime-Opposition Bargaining Game}
\begin{itemize}
\item Violence is the final arbiter in authoritarian politics
\item Regime-opposition interaction is best modeled as a bargaining game, similar to the bargain between two sovereign states with the option of going to war (Fearon 1995)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Regime-Opposition Bargaining Game}
\centering
\begin{itemize}
\item Negotiation about the share $x$ ($0 < x < 1$) of a good given to the opposition
\item Violence costs the autocrat $c_A$ and the opposition $c_O$
\item Expected utility depends on the probability of the opposition winning, $p$
\item<2-> Violence should never happen since $x$ that falls within the bargaining range $(p - c_O, p + c_A)$ is preferable to both sides
\end{itemize}
\includegraphics[width=0.7\textwidth]{general_model}
\end{frame}

@@

\begin{frame}
\frametitle{Regime-Opposition Bargaining Game}
However, authoritarian legislature solves all of these issues
\begin{itemize}
\item<1> (Information Asymmetry) Elections and legislative session provide information about both sides' capacity
\item<2> (Small Bargaining Range) Cost of violent uprising and repression is increased relative to negotiation
\item<3> (Unit indivisibility) Negotiations over multiple issues in the legislature enable side payments
\end{itemize}
\end{frame}
\section{Experimental Design}

\begin{frame}
\frametitle{Business in Vietnam}
\end{frame}

\begin{frame}
\frametitle{Experimental Design}

@@

\frametitle{Checking Experimental Assumption}
\centering
\begin{itemize}
\item<1-2> Balance between the Treated and the Control
\item<3> Same response rate between the Treated and the Control
\item<4-5> Balance between Respondents and Non-Respondents
\end{itemize}

@@

\only<2,5>{\adjustbox{max height=0.3\textheight,

@@

}}

@@

\only<5>{\adjustbox{max height=0.3\textheight,

@@

\begin{frame}
\frametitle{Empirical Strategy}
\begin{itemize}
\item Create short panels of four country years
\item Treatment panel: no legislature in the first year, legislature in the next three years
\item Control panel: no legislature throughout the panel
\item Match panels based on the co-variates of the first years
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Matching Result}
\centering
\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
           max width=\textwidth}{
\begin{tabular}{lrrlrrrl}
  \hline
 & \multicolumn{3}{c}{Pre-Match} &   \multicolumn{3\textbf{}}{c}{Post-Match} \\
Covariate & Treated & Control & p-value & Treated & Control & p-value &  \\ 
  \hline
Ethnic Fractionalization & 0.61 & 0.59 & 0.59 & 0.61 & 0.60 & 0.81 &  \\ 
Violence (Goldstein score) & -4.50 & -4.05 & 0.51 & -4.50 & -4.49 & 0.94 &  \\ 
$\text{Violence}^2$ & 29.84 & 23.22 & 0.34 & 29.84 & 29.03 & 0.65 &  \\ 
Regime duration (years) & 12.08 & 34.30 & 0.00*** & 12.08 & 12.71 & 0.71 &  \\ 
$\text{Regime duration}^2$ & 278.00 & 2783.57 & 0.00** & 278.00 & 287.38 & 0.89 &  \\ 
Military & 0.08 & 0.06 & 0.67 & 0.08 & 0.12 & 0.57 &  \\ 
Monarchy & 0.04 & 0.25 & 0.00*** & 0.04 & 0.04 & 1.00 &  \\ 
Party & 0.29 & 0.48 & 0.07* & 0.29 & 0.29 & 1.00 &  \\ 
log(gdp) & 22.65 & 23.95 & 0.00*** & 22.65 & 22.78 & 0.67 &  \\ 
log(gdp per capita) & 7.63 & 8.58 & 0.00*** & 7.63 & 7.65 & 0.95 &  \\ 
Military expenditure (\%GDP) & 2.44 & 4.34 & 0.00*** & 2.44 & 2.40 & 0.89 &  \\
Land (1000 $\text{km}^2$)& 760.22 & 1674.68 & 0.00*** & 760.21 & 783.37 & 0.80 &  \\ 
Population (million) & 22.62 & 140.73 & 0.00*** & 22.62 & 21.74 & 0.90 &  \\
Resource Export (\%GDP) & 14.79 & 22.64 & 0.03** & 14.79 & 14.16 & 0.72 &  \\ 
Resource $\times$ Ethnic & 8.61 & 14.43 & 0.01** & 8.61 & 8.33 & 0.82 & \\
  \hline
\end{tabular}
}
\end{frame}

\begin{frame}
\frametitle{Matching Result}
\centering
\adjustbox{max height=\dimexpr\textheight-5.5cm\relax,
           max width=\textwidth}{
\begin{tabular}{lrlr}
  \hline
 \multicolumn{2}{c}{Treatment} &   \multicolumn{2}{c}{Control} \\
Country & Year & Country & Year \\ 
  \hline
Algeria & 1996 & Sudan & 1992 \\ 
  Angola & 1992 & Angola & 2000 \\ 
  Azerbaijan & 1992 & Uganda & 1991 \\ 
  Belarus & 2004 & Belarus & 2000 \\ 
  Cambodia & 1993 & Laos & 1999 \\ 
  Central African Republic & 2005 & Uganda & 2001 \\ 
  Chad & 1997 & Central African Republic & 1992 \\ 
  Congo, Republic & 2002 & Nigeria & 1994 \\ 
  Congo, Dem Rep & 2006 & Congo, Dem Rep & 1996 \\ 
  Ethiopia & 1995 & Ethiopia & 1993 \\ 
  Gambia & 1996 & Belarus & 2001 \\ 
  Ghana & 1995 & Belarus & 2000 \\ 
  Jordan & 1993 & Swaziland & 2007 \\ 
  Kazakhstan & 1995 & Sudan & 1994 \\ 
  Kenya & 1992 & Laos & 1997 \\ 
  Kyrgyzstan & 1995 & Belarus & 1998 \\ 
  Pakistan & 2002 & Algeria & 1993 \\ 
  Rwanda & 2003 & Rwanda & 1999 \\ 
  Sudan & 2000 & Sudan & 2006 \\ 
  Tajikistan & 1995 & Belarus & 1999 \\ 
  Tanzania & 1995 & Sierra Leone & 1992 \\ 
  Togo & 1994 & Togo & 1991 \\ 
  Uganda & 2006 & Uganda & 1998 \\ 
  Uzbekistan & 1999 & Ethiopia & 1993 \\ 
   \hline
\end{tabular}
}
\end{frame}

\begin{frame}
\frametitle{Multilevel model}
\begin{alignat*}{2}
&{event}_i &&\sim N(\alpha^{countryyear}_{j[i]} + A \cdot \text{sector}_i, \sigma^2_{event}) \\
&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{legislature}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
&\beta_k^{country} &&\sim N(\delta_0 + \delta_{ethnic} \cdot \text{ethnic fraction}_k + D \cdot \text{region}, \sigma_\beta^2) 
\end{alignat*}
where
\begin{itemize}
\item $\text{sector}_i$: fundamentalist, popular protest, insurgent, etc.
\item $X_j$: log(GDP), log(GDP percap), resource rent, military expenditure, regime duration, type of autocracy
\end{itemize}
\end{frame}
